Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-10-03 paper.tex
modify until alpha-Eg relation

%
%
Using these relations, we show the calculated
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$ in the bottom panels of
Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
reach convergence when $L$ exceeds 10 \AA and 15 \AA, respectively.
{\color{red} Convergence plot in SI} Such result is in good agreement
with the spatially localized induced dipole moment of a 2D materials
as shown in Supplementary Figure~\ref{SI-fig:rho-profile}. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
panels in Fig.\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$
(Fig. \ref{fig-1}\textbf{d}-\textbf{e}).
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Such relations can also be used to remove the dependence on $L$ for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
lattice-independent electronic polarizability
$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
respectively (details see Supplementary Section \ref{SI-ssec:gw}).
%
% 
% 
% 
% 
These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
More discussions about the choice of the
2D polarizability, comparison with other methods, simulations at the
frequency-dependent domain can be found in Supplementary Section
\ref{SI-ssec:gw}.

\subsection{Comparison with effective dielectric model}
\label{sec:comp-with-effect}

@@

As a consequence of Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, we demonstrate that other quantities are
intrinsically related to the polarizability.  Using random phase
approximation (RPA) theory \cite{Adler_1962} within the
$\mathbf{k} \cdot \mathbf{p}$ formalism\cite{kittel_2005_introduction}
(see Supplementary Section \ref{SI-sec:theory-1} for details), we show
that $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ can be written as:
\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &=C^{\parallel} E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & =C^{\perp} \delta
where $E_{\mathrm{g}}$ is the minimal electronic bandgap, $\delta$ is
the intrinsic thickness of the layer (Fig. \ref{fig-1}{\textbf a}), and
$C^{\parallel} = {\displaystyle \frac{Ne^2}{2 \pi}}$ \cite{Jiang_2017_Eg_Eb}, where
$N$ corresponds to the degeneracy of the bands associated with
$E_{\mathrm{g}}$, and $C^{\perp} = {\varepsilon_{0}}$.
% \todo[inline]{The previous expressions for the coefficients are
  % wrong. Please see the version in SI}
Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and
\ref{eq:2D-Moss-perp}, they generalize a direct relationship between
the polarizability and the electronic and structural properties for
any 2D material in a new framework.  We show that these equations are
valid for the current library of known layered materials involving
different lattice symmetry, element composition, optical and
electronic properties.
A high-throughput screening performed on different families of TMDCs
(MX\(_{\text{2}}\), where M is a metal in groups 4, 6, 10, and X=O, S,
Se, Te) and phases (P\(\bar{6}\)m2, P3m1), metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
and thin layer organic-inorganic perovskites (ABX$_{3}$)
(Fig. \ref{fig-3}{\textbf a}) shows that our method enables full
correlation between these disparate variables.  Figure
\ref{fig-3}{\textbf b} compares the calculated fundamental bandgap
$E_{\mathrm{g}}$ (blue dots) and 2D electronic polarizabilities (bar
plots) of all the 2D materials investigated, covering a wide spectrum
range from far-infrared to ultraviolet.  Note from dimension analysis,
it is more intuitive to express the polarizability as
$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases, while no apparent
correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
$E_{\mathrm{g}}$ is observed (see Supplementary Section
\ref{SI-sec:pol-2D-Eg}).  We then examine Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} using the polarizabilities by
first-principle calculations.  Figure \ref{fig-3}{\textbf c} shows
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
materials investigated (circle dots).  A linear regression coefficient
of $R^{2}=0.84$ indicates a strong correlation between bandgaps and
polarizabilities as predicted in Eq. \ref{eq:2D-Moss-para}.  We also
discover that the linearity between
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
bandgap is calculated using the HSE06 hybrid
functional\cite{Heyd_2005} compared with that from
Perdew--Burk--Ernzerhof (PBE)
functional%exchange correlation functional
(see Supplementary Section \ref{SI-sec:pol-2D-Eg} and Supplementary
Figure \ref{SI-fig:alpha-Eg-diff}) which suggests that higher levels
of theory are needed to predict bandgaps. See Supplementary Section
\ref{SI-sec:gpaw} for a benchmark of Eqs.~\ref{eq:2D-Moss-para} and
\ref{eq:2D-Moss-perp} using different bandgaps, databases, and levels
of calculation.

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha_{\mathrm{2D}}^{\parallel}$ and
  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.
  % HSE06 functional is used in all plots.
}
\end{figure}

>>>>

%
%
Using these relations, we show the calculated
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$ in the bottom panels of
Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
reach convergence when $L$ exceeds 10 \AA and 15 \AA, respectively.
{\color{red} Convergence plot in SI} Such result is in good agreement
with the spatially localized induced dipole moment of a 2D materials
as shown in Supplementary Figure~\ref{SI-fig:rho-profile}. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
panels in Figure\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$
(Figure \ref{fig-1}\textbf{d}-\textbf{e}).
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Such relations can also be used to remove the dependence on $L$ for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
lattice-independent electronic polarizability
$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
respectively (details see Supplementary Section \ref{SI-ssec:gw}).
%
% 
% 
% 
% 
These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
More discussions about the choice of the
2D polarizability, comparison with other methods, simulations at the
frequency-dependent domain can be found in Supplementary Section
\ref{SI-ssec:gw}.

\subsection{Comparison with effective dielectric model (EDM)}
\label{sec:comp-with-effect}

@@

For bulk materials, pioneering works from the 1950s have demonstrated
empirical equations between $\varepsilon$ and the bandgap
$E_{\mathrm{g}}$, including the
Moss~\cite{Moss_1950_relation,Moss_1985_n_Eg,Finkenrath_1988} or
Ravindra~\cite{Ravindra_1980_model,Ravindra_1979_eps_Eg} relations.
Such universal relations, if exist in the context of
$\alpha_{\mathrm{2D}}$, would be of high importance for studying and
predicting the screening of 2D materials.  Inspired by the random
phase approximation (RPA) theory \cite{Adler_1962} within the
$\mathbf{k} \cdot \mathbf{p}$
formalism\cite{kittel_2005_introduction,Jiang_2017_Eg_Eb}, we propose the universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
depending on the electronic and geometric information of a 2D material (see
Supplementary Section \ref{SI-sec:theory-1} for details):
% \begin{subequations}
% \begin{eqnarray}
% \label{eq:2D-Moss-para}
  % &\alpha_{\mathrm{2D}}^{\parallel} &=C^{\parallel} E_{g}^{-1} \\
  % \label{eq:2D-Moss-perp}
  % &\alpha_{\mathrm{2D}}^{\perp} & =C^{\perp} \hat{\delta}_{\mathrm{2D}}
% \end{eqnarray}
% \end{subequations}
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &E_{\mathrm{g}} &= C^{\parallel} \alpha_{\mathrm{2D}}^{\parallel} \\
  \label{eq:2D-Moss-perp}
  &\hat{\delta}_{\mathrm{2D}} & = C^{\perp} \alpha_{\mathrm{2D}}^{\perp} 
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the fundamental electronic bandgap and
$\hat{\delta}_{\mathrm{2D}}$ is the intrinsic thickness of the 2D
layer, with coefficients
$C^{\parallel} = {\displaystyle \frac{2 \pi}{Ne^2}}$
\cite{Jiang_2017_Eg_Eb}, where $N$ is a pre-factor associated with the
band degeneracy, and $C^{\perp} = {\varepsilon_{0}}^{-1}$. It is worth
noting, unlike the parameter $\delta_{\mathrm{2D}}$ that is
artificially assigned within the EDM picture (see previous section),
$\hat{\delta_{\mathrm{2D}}}$ can be uniquely defined by
$\alpha_{\mathrm{2D}}^{\parallel}$, a quantity that can be
computationally and experimentally determined. Despite of the
simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp},
they generalize direct relationships between the electronic polarizability and
the electronic / structural properties for any 2D material in a new
framework.

Next, we show that these equations are valid for the current
library of known layered materials involving different lattice
symmetry, element composition, optical and electronic properties.
%
A high-throughput screening performed on different families of TMDCs
(MX\(_{\text{2}}\), where M is a metal in groups 4, 6, 10, and X=O, S,
Se, Te) and phases (P\={6}m2, P3m1), metal monochalcogenides
(Ga\textsubscript{2}S\textsubscript{2},
Ga\textsubscript{2}Se\textsubscript{2}), cadmium halides (CdX$_2$,
X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
(fluorographene (C\textsubscript{2}F\textsubscript{2}), graphane
(C\textsubscript{2}H\textsubscript{2})), phosphorene
(P\textsubscript{4}) and thin layer organic-inorganic perovskites
(ABX\textsubscript{3}) (Figure \ref{fig-3}{\textbf a}) shows that our
method enables full correlation between these disparate variables.
Figure \ref{fig-3}{\textbf b} compares the calculated fundamental
bandgap $E_{\mathrm{g}}$ (blue dots) and 2D electronic
polarizabilities (bar plots) of all the 2D materials investigated,
covering a wide spectrum range from far-infrared to ultraviolet.  Note
from dimension analysis, it is more intuitive to express the
polarizability as $\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$,
which has unit of \AA{}. We find that
$\alpha_{\mathrm{2D}}^{\parallel}$ has a general descending trend when
$E_{\mathrm{g}}$ increases, while no apparent correlation between
$\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is observed (see
Supplementary Section \ref{SI-sec:pol-2D-Eg}).  We then examine
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
polarizabilities by first-principle calculations.  Figure
\ref{fig-3}\textbf{c} shows
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
materials investigated (circle dots) at HSE06 level.  A linear
regression coefficient of $R^{2}=0.84$ indicates a strong correlation
between bandgaps and polarizabilities as predicted in
Eq. \ref{eq:2D-Moss-para}.  We also discover that the linearity
between $(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
bandgap is calculated using the HSE06 hybrid functional compared with
that from PBE exchange-correlation functional (see Supplementary
Section \ref{SI-sec:pol-2D-Eg} and Supplementary Figure
\ref{SI-fig:alpha-Eg-diff}) which suggests that higher levels of
theory are needed to precisely predict bandgaps.  A detailed benchmark
of Eqs.~\ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using
different bandgaps, databases, and levels of calculation can be seen
in Supplementary Section~\ref{SI-sec:gpaw}.

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS\textsubscript{2} in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha_{\mathrm{2D}}^{\parallel}$ and
  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.
  % HSE06 functional is used in all plots.
}
\end{figure}
